\section{Game Description}

	\begin{frame}
		\frametitle{The Game} 
		
		\begin{itemize}
			\item
				4 people in group for 10 periods
			\item
				Each period has two stages:
				\begin{enumerate}
					\item 
						investment stage
					\item
						contribution stage
				\end{enumerate}
			\item
				Endowments of 10 for each player in each period
		\end{itemize}
		
	\end{frame}

	\begin{frame}
		\frametitle{Investment Stage} 
		
		\begin{itemize}
			\item
				Players can increase their contribution productivity from the starting value of 0.30
			\item
				Vote (median rule) to determine the amount each player in the group will invest in increasing contribution productivity
			\item
				Contribution productivity increases by 0.01 multiplied by the investment
		\end{itemize}
	
		\[
			\text{Contribution productivity} = M_t = M_{t-1} + 0.01 \cdot I_t
		\]
		\[
			\text{for } t = [1..10]
		\]
		\[
			M_0 = 0.3
		\]
		
		
	\end{frame}

	\begin{frame}
		\frametitle{Contribution Stage} 
		
		Players decide how to allocate their remaining money between private consumption and public good. \\~\\
		
		Payoff:
		\[
			\pi_{it} = \omega - I_t - c_{it} + M_t \sum c_{jt}
		\]
		
		
	\end{frame}

	\begin{frame}
		\frametitle{Example} 
		Example ($M_0 = 0.3$):
		\begin{block}{Table}
			\begin{center}
				\begin{tabular}{ | c | c | c | c | c | c | c |}
					\hline
					Players	& $\omega$	& $I_t$						& $M_t$					& $C_{it}$	& $M_t \sum c_{jt}$			& $\pi_{it}$	\\ \hline
					1		& $10$		& \multirow{4}{*}{$3$}		& \multirow{4}{*}{0.33}	& $7$		& \multirow{4}{*}{$4.95$}	& $4.95$		\\ 
					2		& $10$		& 							&						& $5$		&							& $6.95$		\\ 
					3		& $10$		& 							&						& $3$		&							& $8.95$		\\ 
					4		& $10$		& 							&						& $0$		&							& $11.95$		\\ \hline
				\end{tabular}
			\end{center}
		\end{block}
	\end{frame}

	\begin{frame}
		\frametitle{Potential Outcomes} 

		\begin{itemize}
			\item
				\textbf{The Lowest Payoff outcome.}
				How would the players act to get the lowest possible payoffs?
				What are the lowest possible payoffs?
			\item
				\textbf{The Nash Equilibrium.}
				What would happen if each player acted in his own interest?
			\item 
				\textbf{The Socially Optimal outcome.}
				How should the players act so that the sum of payoffs is maximized?
				What is this sum of payoffs?
		\end{itemize}
	\end{frame}